### 2018-08-08 UnintentionalStateConflict/paper3/sections/Formalization.tex
Theorem 4 proof (unfinished)

\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
	If $\mu | t \to \mu' | t'$ and $\mu | t \to \mu'' | t''$, then $t' = t''$ and $\mu' = \mu''$.
\end{theorem}
\begin{proof}	
The Proof is done by induction on a derivation of $t \to t'$, following the book  \emph{TAPL}.
\begin{itemize}
	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(S-Invk)}, then we know that $t$ has the form $\left((J)\new{I}\right).m(\overline{v})$ with $I, J, m$ determined. Now it is obvious that the last rule in the derivation of $t \to t''$ should also be \textsc{(S-Invk)} with the same $I, J, m$. Since $\mbody(m, I, J)$ is a \emph{function} that given the same input will calculate the same result, we know the two induction results are the same, thus $t' = t''$ is immediately proved.

	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Receiver)}, then $t$ has the form $e_0.m(\overline{e})$ and $e_0 \to e_0'$. Since $e_0$ is not a value, the last rule used in $t \to t''$ has to be \textsc{(C-Receiver)} (other rules do not match) too. Assume in the reduction $t \to t''$, $e_0 \to e_0''$, thus $e_0'.m(\overline{e}) = e_0''.m(\overline{e})$. Thus, $t' = t''$ proved.

	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-StaticType)}, then $t$ is fixed to be $\new{I}$. The last rule used in $t \to t''$  has to be \textsc{(C-StaticType)}, and obviously, $t' = t'' = (I)\new{I}$.

	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-FReduce)}, then $t$ has the form $(I)e$ and $e \to e'$. The last rule used in $t \to t''$ cannot be \textsc{(C-StaticType)} because it requires $t$ to be $\new{I}$; it can neither be \textsc{(C-AnnoReduce)} because it requires $t$ to be $(I)((J)\new{K})$ where $(J)\new{K}$ is already a value. So the last rule used in $t \to t''$ can only be \textsc{(C-FReduce)} (other rules do not match). Assume in the reduction $t \to t''$, $e \to e''$, and $(I)e \to (I)e''$. By induction hypothesis, $e' = e''$, thus $t' = t''$ proved.

	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-AnnoReduce)}, then the form of $t$ is fixed to be $(I)((J)\new{K})$. Since $(I)((J)\new{K})$ is not reducible, the rule \textsc{(C-FReduce)} does not apply. The only rule applies in $t \to t''$ is \textsc{(C-AnnoReduce)}. Thus $t' = t'' = (I)\new{K}$ proved.

	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Args)}, then $t$ has the form $v.m(..., e, ...)$ and $e \to e'$. The last rule used in $t \to t''$ cannot be \textsc{(S-Invk)} because it requires all arguments to be values. Thus only \textsc{(C-Args)} applies to $t \to t''$. Assume in the reduction $t \to t''$, $e \to e''$. By induction hypothesis, $e' = e''$, thus $v.m(..., e', ...) = v.m(..., e'', ...)$, thus $t' = t''$ proved.
\end{itemize}
\end{proof}

>>>>

\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
	If $\mu \mid t \to \mu' \mid t'$ and $\mu \mid t \to \mu'' \mid t''$, then $t' = t''$ and $\mu' = \mu''$.
\end{theorem}
\begin{proof}	
The Proof is done by induction on a derivation of $\mu \mid t \to \mu' \mid t'$, following the book  \emph{TAPL}.
\begin{itemize}
	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Invk)}, then we know that $t$ has the form $(J)o.m(\overline{v})$ with $\mu(o) = \newI{I}{...}$, $I, J, m$ determined. Now it is obvious that the last rule in the derivation of $\mu \mid t \to \mu'' \mid t''$ should also be \textsc{(E-Invk)} with the same $I, J, m$. Since $\mbody(m, I, J)$ is a \emph{function} that given the same input will calculate the same result, we know the two induction results are the same, thus $t' = t''$ is immediately proved. Also from the rule \textsc{(E-Invk)}, we know that $\mu$ is unchanged, thus $\mu' = \mu'' = \mu$ is also proved.

	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-New)}, then the form of $t$ is fixed to be $\newI{I}{\overline{v}}$. The only rule applies in $\mu \mid t \to \mu'' \mid t''$ is also \textsc{(E-New)}. From the rule \textsc{(E-New)} we know that $t' = t'' = (I)o$ and $\mu' = \mu'' = \mu, o \to \newI{I}{\overline{v}}$ proved.

	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Cast)}, then the form of $t$ is fixed to be $(I)((J)o)$. Since $(J)o$ is not reducible, the only rule applies in $\mu \mid t \to \mu'' \mid t''$ is \textsc{(E-Cast)}. Also from the rule \textsc{(E-Cast)} we know that $\mu$ is unchanged, thus $t' = t'' = (I)o$ and $\mu' = \mu'' = \mu$ proved.

	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Let)}, then the form of $t$ is fixed to be $\mylet{I}{x}{o}{e}$. And the only rule applies in $\mu \mid t \to \mu'' \mid t''$ is \textsc{(E-Let)}. Also from the rule \textsc{(E-Cast)} we know that $\mu$ is unchanged, thus $t' = t'' = e[(I)o/x]$ and $\mu' = \mu'' = \mu$ proved.

	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Getter)}, then the form of $t$ is fixed to be $(J)o.f()$. For the second reduction $\mu \mid t \to \mu'' \mid t''$, the rule \textsc{(E-Setter)} does not apply because the number of parameters does not match. Also the rule \textsc{(E-Invk)} does not match because the precondition $!validGetter(m, I, J)$ is not satisfied. The only rule applies  is the rule \textsc{(E-Getter)}. Also from the rule \textsc{(E-Getter)} we know that $\mu$ is unchanged, thus $t' = t'' = (I_F)o_i$ and $\mu' = \mu'' = \mu$ proved.

	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Setter)}, then the form of $t$ is fixed to be $(J)o.SET_f((I')o)$. Then for the second reduction $\mu \mid t \to \mu'' \mid t''$, the rule \textsc{(E-Getter)} does not apply because the number of parameters does not match. Also the rule \textsc{(E-Invk)} does not match because the precondition $!validSetter(m, I, J)$ is not satisfied. The only rule applies is the rule \textsc{(E-Setter)}. And from the rule \textsc{(E-Setter)}, we know that $t' = t'' = (I)o$. Assume in the first derivation $\mu \mid t \to \mu' \mid t'$, $\mu = \mu_0, o \to \newI{I}{o_1,...,o_i,...,o_n}, \mu' = \mu_0, o \to \newI{I}{o_1,...,o',...,o_n}$, then in the second derivation $\mu \mid t \to \mu'' \mid t''$, $\mu = \mu_0, o \to \newI{I}{o_1,...,o_i,...,o_n}, \mu'' = \mu_0, o \to \newI{I}{o_1,...,o',...,o_n} = \mu'$. Proved.

	\item \item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-CTX)}, 
\end{itemize}
\end{proof}
